Step1_LoadData

### 2024-07-18 ProxySelection.Rmd
all results

# Get important features
rf_importance <- importance(rf_model)
important_features_rf <- rownames(rf_importance)[order(rf_importance[, 1], decreasing = TRUE)]

# Select features
fs_rf <- important_features_rf[important_features_rf %in% proxy.list]
proxy_rf <- paste0(fs_rf, collapse = "+")
form_rf <- paste0(c(covform, proxy_rf), collapse = "+")
formula_rf <- as.formula(paste0("exposure", "~", form_rf))

@@

# Get important features
important_features_rfe <- predictors(results)

# Select features
fs_rfe <- important_features_rfe[important_features_rfe %in% proxy.list]
proxy_rfe <- paste0(fs_rfe, collapse = "+")
form_rfe <- paste0(c(covform, proxy_rfe), collapse = "+")
formula_rfe <- as.formula(paste0("exposure", "~", form_rfe))

W.out_rfe <- weightit(formula_rfe, 
                      data = hdps.data, 
                      estimand = "ATE",
                      method = "ps")

hdps.data$ps_rfe <- W.out_rfe$ps
hdps.data$w_rfe <- W.out_rfe$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
fit_rfe <- glm(out.formula,
               data = hdps.data,
               weights = W.out_rfe$weights,
               family= binomial(link = "logit"))
summary_rfe <- summary(fit_rfe)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci_rfe <- confint(fit_rfe, level = 0.95)["exposure", ]
sum_ci_rfe <- c(exp(summary_rfe[1]), summary_rfe, ci_rfe)
names(sum_ci_rfe) <- c("Odds Ratio",
                       "Estimate",
                       "Std. Error",
                       "Pr(>|z|)",
                       "2.5 %",
                       "97.5 %")

end_time <- Sys.time()
elapsed_time_rfe <- as.numeric(difftime(end_time, start_time, units = "secs"))

print("How many proxy variables are in common?")
paste("There are", length(fs_rfe), "features selected by RFE")
paste(length(fs_rfe[fs_rfe %in% fs.bross]), "of the", length(fs_rfe), 
      "are also selected by the bross formula method")

print("The Odds Ratio by RFE")
sum_ci_rfe
print("Elapsed time for RFE:")
elapsed_time_rfe
```

>>>>

# Get important features
rf_importance <- importance(rf_model)
important_features_rf <- rownames(rf_importance)[order(rf_importance[, 1], decreasing = TRUE)]
```

```{r rf2, warning=FALSE, cache=TRUE}
# Select features
fs_rf <- important_features_rf[important_features_rf %in% proxy.list]
proxy_rf <- paste0(fs_rf, collapse = "+")
form_rf <- paste0(c(covform, proxy_rf), collapse = "+")
formula_rf <- as.formula(paste0("exposure", "~", form_rf))

@@

# Get important features
important_features_rfe <- predictors(results)
```

```{r rfe2, warning=FALSE, cache=TRUE}
# Select features
# fs_rfe <- important_features_rfe[important_features_rfe %in% proxy.list]
# proxy_rfe <- paste0(fs_rfe, collapse = "+")
# form_rfe <- paste0(c(covform, proxy_rfe), collapse = "+")
# formula_rfe <- as.formula(paste0("exposure", "~", form_rfe))
# 
# W.out_rfe <- weightit(formula_rfe, 
#                       data = hdps.data, 
#                       estimand = "ATE",
#                       method = "ps")
# 
# hdps.data$ps_rfe <- W.out_rfe$ps
# hdps.data$w_rfe <- W.out_rfe$weights
# out.formula <- as.formula(paste0("outcome", "~", "exposure"))
# fit_rfe <- glm(out.formula,
#                data = hdps.data,
#                weights = W.out_rfe$weights,
#                family= binomial(link = "logit"))
# summary_rfe <- summary(fit_rfe)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
# ci_rfe <- confint(fit_rfe, level = 0.95)["exposure", ]
# sum_ci_rfe <- c(exp(summary_rfe[1]), summary_rfe, ci_rfe)
# names(sum_ci_rfe) <- c("Odds Ratio",
#                        "Estimate",
#                        "Std. Error",
#                        "Pr(>|z|)",
#                        "2.5 %",
#                        "97.5 %")
# 
# end_time <- Sys.time()
# elapsed_time_rfe <- as.numeric(difftime(end_time, start_time, units = "secs"))
# 
# print("How many proxy variables are in common?")
# paste("There are", length(fs_rfe), "features selected by RFE")
# paste(length(fs_rfe[fs_rfe %in% fs.bross]), "of the", length(fs_rfe), 
#       "are also selected by the bross formula method")
# 
# print("The Odds Ratio by RFE")
# sum_ci_rfe
# print("Elapsed time for RFE:")
# elapsed_time_rfe
```
